Trip Summary ITHIM-R

### 2021-03-24 code/producing_trips_rd/trip-summary.Rmd
Adding guess_max option when reading datasets

```{r,  comment=NA, message=FALSE, warning=FALSE, prompt=FALSE, cache=FALSE, echo=F}
trip <- read_csv("../../data/local/buenos_aires/buenos_aires_trip.csv")
quality_check(trip)
trip_summary$Buenos_Aires <- value

trip <- read_csv("../../data/local/sao_paulo/sao_paulo_trip.csv")
quality_check(trip)
trip_summary$Sao_Paulo <- value

trip <- read_csv("../../data/local/belo_horizonte/belo_horizonte_trip.csv")
quality_check(trip)
trip_summary$Belo_Horizonte <- value

trip <- read_csv("../../data/local/mexico_city/mexico_city_trip.csv")
quality_check(trip)
trip_summary$Mexico <- value

trip <- read_csv("../../data/local/bogota/bogota_trips.csv")
quality_check(trip)
trip_summary$Bogota <- value

trip <- read_csv("../../data/local/santiago/santiago_trip.csv")
quality_check(trip)
trip_summary$Santiago <- value

trip <- read_csv("../../data/local/vizag/vizag_trip.csv")
quality_check(trip)
trip_summary$Visakhapatnam <- value

trip <- read_csv("../../data/local/delhi/delhi_trip.csv")
quality_check(trip)
trip_summary$Delhi <- value

trip <- read_csv("../../data/local/bangalore/bangalore_trip.csv")
quality_check(trip)
trip_summary$Bangalore <- value

trip <- read_csv("../../data/local/accra/accra_trip.csv")
quality_check(trip)
trip_summary$Accra <- value

trip <- read_csv("../../data/local/cape_town/cape_town_trip.csv")
quality_check(trip)
trip_summary$Cape_Town <- value

>>>>

```{r,  comment=NA, message=FALSE, warning=FALSE, prompt=FALSE, cache=FALSE, echo=F}
trip <- read_csv("../../data/local/buenos_aires/buenos_aires_trip.csv",
                 guess_max = 100000)
quality_check(trip)
trip_summary$Buenos_Aires <- value

trip <- read_csv("../../data/local/sao_paulo/sao_paulo_trip.csv",
                 guess_max = 100000)
quality_check(trip)
trip_summary$Sao_Paulo <- value

trip <- read_csv("../../data/local/belo_horizonte/belo_horizonte_trip.csv",
                 guess_max = 100000)
quality_check(trip)
trip_summary$Belo_Horizonte <- value

trip <- read_csv("../../data/local/mexico_city/mexico_city_trip.csv",
                 guess_max = 100000)
quality_check(trip)
trip_summary$Mexico <- value

trip <- read_csv("../../data/local/bogota/bogota_trips.csv",
                 guess_max = 100000)
quality_check(trip)
trip_summary$Bogota <- value

trip <- read_csv("../../data/local/santiago/santiago_trip.csv",
                 guess_max = 100000)
quality_check(trip)
trip_summary$Santiago <- value

trip <- read_csv("../../data/local/vizag/vizag_trip.csv",
                 guess_max = 100000)
quality_check(trip)
trip_summary$Visakhapatnam <- value

trip <- read_csv("../../data/local/delhi/delhi_trip.csv",
                 guess_max = 100000)
quality_check(trip)
trip_summary$Delhi <- value

trip <- read_csv("../../data/local/bangalore/bangalore_trip.csv",
                 guess_max = 100000)
quality_check(trip)
trip_summary$Bangalore <- value

trip <- read_csv("../../data/local/accra/accra_trip.csv",
                 guess_max = 100000)
quality_check(trip)
trip_summary$Accra <- value

trip <- read_csv("../../data/local/cape_town/cape_town_trip.csv",
                 guess_max = 100000)
quality_check(trip)
trip_summary$Cape_Town <- value
